Placeholder for article 3

### 2025-01-13 analysis/paper/paper.qmd
Same as previous commit. Forgot to save :p

@@

```{r}
#| label: fig-ratiotd
#| fig-cap: Plotted ratios of tools-to-debitage by chert types (x axis) and assemblage (colour). Distance to source groups (local and non-local) are marked by different shapes.

>>>>

```{r}
#| label: fig-ratiobc
#| fig-cap: Plotted ratios of blanks-to-core by assemblage and by chert type. All local cherts were grouped in a single category "Local", while non-local cherts maintained their individual IDs.

gravettian_ratiobc_b <-gravettian_ratiobc %>%
  filter(`Blank/Core` != "Inf") %>% 
  dplyr::mutate("Assemblage" = "Gravettian") %>% 
  select(Assemblage, RMTYPE, `Blank/Core`)
proto_ratiobc_b <- proto_ratiobc %>% 
  filter(`Blank/Core` != "Inf") %>% 
  dplyr::mutate("Assemblage" = "Proto-Solutrean") %>% 
  select(Assemblage, RMTYPE, `Blank/Core`)
solutrean_ratiobc_b <- solutrean_ratiobc %>% 
  filter(`Blank/Core` != "Inf") %>% 
  dplyr::mutate("Assemblage" = "Solutrean") %>% 
  select(Assemblage, RMTYPE, `Blank/Core`)
ratio_blankcore <- bind_rows(gravettian_ratiobc_b, proto_ratiobc_b,solutrean_ratiobc_b)

# Scatterplot with local vs non-local RM Types
ratio_blankcore |>
  dplyr::mutate(Source = case_when(
    RMTYPE == "TYPE 1" | RMTYPE == "TYPE 2" | RMTYPE == "TYPE 3" | RMTYPE == "TYPE 4" | RMTYPE == "TYPE 5" ~ "Local",
    RMTYPE == "TYPE 6" ~ "T6",
    RMTYPE == "TYPE 7" ~ "T7",
    RMTYPE == "TYPE 8" ~ "T8",
    RMTYPE == "TYPE 9" ~ "T9",
    RMTYPE == "TYPE 10" ~ "T10",
    RMTYPE == "TYPE 11" ~ "T11",
    TRUE ~ RMTYPE)) |>
  mutate(Source = factor(Source, levels = c("Local", "T6","T7", 
                                        "T8", "T9", "T10", "T11", "TL"))) |>
  ggplot(aes(x=Assemblage, y=`Blank/Core`, colour = Source)) +
  geom_point(size=3) +
  coord_cartesian(clip = "off") +
  scale_colour_manual(values = c("#D49B54", "#8B6969", "#CDAF95", "#2B4F60",
                              "#8B7D6B", "#BDD2B6", "#798777", "#BDC7C9"))
```

@@

```{r}
#| label: fig-ratiotd
#| fig-cap: Plotted ratios of tools-to-debitage by assemblage and by chert type. All local cherts were grouped in a single category "Local", while non-local cherts maintained their individual IDs.
